Brother, can you spare a manufacturing job? White Voters' reaction to Deindustrialization

### 2021-11-30 rCode/Draft.Rmd
small change

---
title: 'bf Brother, can you spare a manufacturing job? White Voters reaction to Deindustrialization'
author: 'Catherine Darin and Zagreb Mukerjee'
date: '11/29/2021'
fontsize: 12pt
output:
  pdf_document: default
urlcolor: red
header-includes:
  - \usepackage{bm}
---

@@

We look at manufacturing employment (NAICS 31-33, see extensions below). Then  compute net change in mfg jobs (long term job loss) from 2004 to 2015, relative to employment in 2004.

We might be worried about endogeneity for manufacturing job losses. So we use a shift-share instrument: we predict job losses per worker with county-level manufacturing as a share of total employment, plus controls.

@@

@@

```{r setup, echo=F, message = F, warning= F}
library(tidyverse)
library(stargazer)
library(sandwich)
library(lmtest)
library(knitr)
library(kableExtra)
library(readxl)
library(scales)
knitr::opts_chunk$set(fig.pos = "!H", out.extra = "")
```

@@

library(tigris)

>>>>

---
title: "Brother, can you spare a manufacturing job? White Voters' reaction to Deindustrialization"
author: 'Catherine Darin and Zagreb Mukerjee'
date: '11/29/2021'
fontsize: 12pt
output:
  pdf_document: default
urlcolor: red
header-includes:
  - \usepackage{bm}
---

@@

We look at total employment and manufacturing employment (NAICS 31-33, see extensions below). We then  compute net change in mfg jobs (long term job loss) from 2004 to 2015, relative to employment in 2004.

We might be worried about endogeneity for manufacturing job losses. So we use a shift-share instrument: we predict net job losses per worker with county-level manufacturing as a share of total employment, plus controls.

@@

## Extension Relative to

@@

```{r setup, echo=F, message = F, warning= F}
library(tidyverse)
library(stargazer)
library(sandwich)
library(lmtest)
library(knitr)
library(kableExtra)
library(readxl)
library(scales)
library(tigris)

knitr::opts_chunk$set(fig.pos = "!H", out.extra = "")
```

@@
